Notes for Week 8/26/2020 - 9/2/2020

### 2021-02-11 notes/graph_regression.tex
Cleaned up notes folder.

\subsubsection{First-order graph Sobolev semi-norm.}
\label{subsec:first_order_graph_sobolev_seminorm}
We begin by upper bounding $f_0^T \Lap_{n,r} f_0$ under the assumption $f_0 \in H^1(\Xset,M)$. We separate this out from the analysis of general $s$ because the regularity conditions we require when $s = 1$ will be meaningfully weaker than when $s > 1$. Specifically, we will assume the kernel $K$ and domain $\Xset$ satisfy conditions~\ref{asmp:kernel} and~\ref{asmp:domain}, respectively.
\begin{enumerate}[label=(K\arabic*)]
	\item
	\label{asmp:kernel}
	$K:[0,\infty) \to [0,\infty)$ is supported on $[0,1]$, and its restriction to $[0,1]$ is Lipschitz. Additionally, it is normalized so that
	\begin{equation*}
	\int_{\Reals^d} K\bigl(\norm{z}\bigr) \,dz = 1.
	\end{equation*}
\end{enumerate}
\begin{enumerate}[label=(P\arabic*)]
	\setcounter{enumi}{2}
	\item 
	\label{asmp:domain}
	The density $p$ is supported on a Lipschitz domain $\Xset$. \textcolor{red}{(TODO 3)}: Formally define a Lipschitz domain.
\end{enumerate}
The former is a relatively mild assumption: the choice of kernel is under the user's control, and moreover~\ref{asmp:kernel} covers many (though certainly not all) common kernel choices. The latter is somewhat more restrictive, but an important point is that we do not require that the domain be \textit{a priori} known in order to formulate our estimators and tests; we will elaborate on this point in Section~\ref{sec:discussion}. In Lemma~\ref{lem:first_order_graph_sobolev_seminorm}, we prove that under these conditions, if the density $p$ is merely upper bounded then~\eqref{eqn:graph_sobolev_seminorm_asymptotic} holds with respect to the first-order graph Sobolev semi-norm.
\begin{lemma}
	\label{lem:first_order_graph_sobolev_seminorm}
	Assume~\ref{asmp:kernel} and~\ref{asmp:domain}, and additionally that $p(x) \leq p_{\max}$ for all $x \in \Xset$. Then, for any $f \in H^1(\Xset,M)$, there exists a constant $C_1 > 0$ which depends only on $\Xset$, $d$, $p_{\max}$ and $K$ such that
	\begin{equation}
	\label{eqn:first_order_graph_sobolev_seminorm}
	f^T \Lap_{n,r} f \leq \frac{C_1}{\delta} n^2 r^{d + 2} M^2
	\end{equation}
	with probability at least $1 - \delta$.
\end{lemma}
The proof of Lemma~\ref{lem:first_order_graph_sobolev_seminorm}, as with all of our proofs, is contained in the Appendix. There are a few remarks worth making regarding Lemma~\ref{lem:first_order_graph_sobolev_seminorm}, but they all apply equally well to our analysis of $f^T\Lap_{{n,r}}^sf$ for $s > 1$, and so we will wait to make them.

@@

\subsubsection{Testing}

Let us define two simple tests, the first using $T_{\LE}$ and the second using $T_{\LS}$. For $b \geq 1$, define the thresholds $\wh{t}_b$ and $\wt{t}_b$ to be
\begin{equation*}
\wh{t}_{b} := \frac{\kappa}{n} + \frac{2b\sqrt{\kappa}}{n},~~ \wt{t}_{b} := \frac{1}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k(G_{n,r}) + 1\bigr)^2} + \frac{2b}{n}\sqrt{\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k(G_{n,r}) + 1\bigr)^4}}.
\end{equation*}
Then let the Laplacian eigenmaps test $\wh{\phi}_{\LE} := \1\bigl\{T_{\LE} \leq \wh{t}_b\bigr\}$, and the Laplacian smoothing test $\wt{\phi}_{\LS} := \1\bigl\{T_{\LS} \leq \wt{t}_b\bigr\}$; clearly the tests $\wh{\phi}_{\LE}$ and $\wt{\phi}_{\LS}$ depend on $b$, but we suppress this notationally. The number $b$ is selected by the user, with the choice made based on the tolerated level of Type I and Type II error. In fact, some standard computations show that the thresholds $\wh{t}_b$ ($\wt{t}_b$) are sufficiently large to control the Type I error of $\wh{\phi}_{\LE}$ ($\wt{\phi}_{\LS}$), 
\begin{equation*}
\Ebb_0\Bigl[\wh{\phi}_{\LE}\Bigr],~~\Ebb_0\Bigl[\wt{\phi}_{\LS}\Bigr] \leq \frac{1}{b^2};
\end{equation*}
we relegate these computations to the appendix (see Lemmas~\ref{lem:le_fixed_graph_testing} and~\ref{lem:ls_fixed_graph_testing}). It remains to show that these tests have small Type II error whenever $f_0$ is separated from $0$ by more than the critical radius $\epsilon_n^{\star}(\mc{H}^s(\Xset,M))$, which we recall from~\eqref{eqn:sobolev_space_testing_critical_radius}. To show this, we proceed in a parallel manner to Section~\ref{subsubsec:first_order_smoothness_estimation}, starting first with the Laplacian eigenmaps test and moving on to the Laplacian smoothing test.

@@

\bibliographystyle{plainnat}
\bibliography{../graph_testing_bibliography}

>>>>

\subsubsection{First-order graph Sobolev semi-norm.}
\label{subsec:first_order_graph_sobolev_seminorm}
We begin by upper bounding $f_0^T \Lap_{n,r} f_0$ under the assumption $f_0 \in H^1(\Xset,M)$. We separate this out from the analysis of general $s$ because the regularity conditions we require when $s = 1$ will be meaningfully weaker than when $s > 1$. Specifically, we will assume the kernel $K$ and domain $\Xset$ satisfy conditions~\ref{asmp:kernel} and~\ref{asmp:domain}, respectively.
\begin{enumerate}[label=(K\arabic*)]
	\item
	\label{asmp:kernel}
	$K:[0,\infty) \to [0,\infty)$ is supported on $[0,1]$, and its restriction to $[0,1]$ is Lipschitz. Additionally, it is normalized so that
	\begin{equation*}
	\int_{\Reals^d} K\bigl(\norm{z}\bigr) \,dz = 1.
	\end{equation*}
\end{enumerate}
\begin{enumerate}[label=(P\arabic*)]
	\setcounter{enumi}{2}
	\item 
	\label{asmp:domain}
	The density $p$ is supported on a Lipschitz domain $\Xset$. \textcolor{red}{(TODO 3)}: Formally define a Lipschitz domain.
\end{enumerate}
The former is a relatively mild assumption: the choice of kernel is under the user's control, and moreover~\ref{asmp:kernel} covers many (though certainly not all) common kernel choices. The latter is somewhat more restrictive, but an important point is that we do not require that the domain be \textit{a priori} known in order to formulate our estimators and tests; we will elaborate on this point in Section~\ref{sec:discussion}. In Lemma~\ref{lem:first_order_graph_sobolev_seminorm}, we prove that under these conditions, if the density $p$ is merely upper bounded then~\eqref{eqn:graph_sobolev_seminorm_asymptotic} holds with respect to the first-order graph Sobolev semi-norm.
\begin{lemma}
	\label{lem:first_order_graph_sobolev_seminorm}
	Assume~\ref{asmp:kernel} and~\ref{asmp:domain}, and additionally that $p(x) \leq p_{\max}$ for all $x \in \Xset$. Then, for any $f \in H^1(\Xset)$, there exists a constant $C_1 > 0$ which depends only on $\Xset$, $d$, $p_{\max}$ and $K$ such that
	\begin{equation}
	\label{eqn:first_order_graph_sobolev_seminorm}
	f^T \Lap_{n,r} f \leq \frac{C_1}{\delta} n^2 r^{d + 2} M^2
	\end{equation}
	with probability at least $1 - \delta$.
\end{lemma}
The proof of Lemma~\ref{lem:first_order_graph_sobolev_seminorm}, as with all of our proofs, is contained in the Appendix. There are a few remarks worth making regarding Lemma~\ref{lem:first_order_graph_sobolev_seminorm}, but they all apply equally well to our analysis of $f^T\Lap_{{n,r}}^sf$ for $s > 1$, and so we will wait to make them.

@@

\subsubsection{Testing}
Let us define two simple tests, the first using $T_{\LE}$ and the second using $T_{\LS}$. For $b \geq 1$, define the thresholds $\wh{t}_b$ and $\wt{t}_b$ to be
\begin{equation*}
\wh{t}_{b} := \frac{\kappa}{n} + \frac{2b\sqrt{\kappa}}{n},~~ \wt{t}_{b} := \frac{1}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k(G_{n,r}) + 1\bigr)^2} + \frac{2b}{n}\sqrt{\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k(G_{n,r}) + 1\bigr)^4}}.
\end{equation*}
Then let the Laplacian eigenmaps test $\wh{\phi}_{\LE} := \1\bigl\{T_{\LE} \leq \wh{t}_b\bigr\}$, and the Laplacian smoothing test $\wt{\phi}_{\LS} := \1\bigl\{T_{\LS} \leq \wt{t}_b\bigr\}$; clearly the tests $\wh{\phi}_{\LE}$ and $\wt{\phi}_{\LS}$ depend on $b$, but we suppress this notationally. The number $b$ is selected by the user, with the choice made based on the tolerated level of Type I and Type II error. In fact, some standard computations show that the thresholds $\wh{t}_b$ ($\wt{t}_b$) are sufficiently large to control the Type I error of $\wh{\phi}_{\LE}$ ($\wt{\phi}_{\LS}$), 
\begin{equation*}
\Ebb_0\Bigl[\wh{\phi}_{\LE}\Bigr],~~\Ebb_0\Bigl[\wt{\phi}_{\LS}\Bigr] \leq \frac{1}{b^2};
\end{equation*}
we relegate these computations to the appendix (see Lemmas~\ref{lem:le_fixed_graph_testing} and~\ref{lem:ls_fixed_graph_testing}). It remains to show that these tests have small Type II error whenever $f_0$ is separated from $0$ by more than the critical radius $\epsilon_n^{\star}(\mc{H}^s(\Xset,M))$, which we recall from~\eqref{eqn:sobolev_space_testing_critical_radius}. To show this, we proceed in a parallel manner to Section~\ref{subsubsec:first_order_smoothness_estimation}, starting first with the Laplacian eigenmaps test and moving on to the Laplacian smoothing test.

@@

\bibliographystyle{plainnat}
\bibliography{../graph_regression_bibliography}

### 2021-02-11 notes/graph_testing.tex
Cleaned up notes folder.

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\Xsetx}{\,dx}
\newcommand{\Xsety}{\,dy}
\newcommand{\Xsetr}{\,dr}
\newcommand{\Xsetxpr}{\,dx'}
\newcommand{\Xsetypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\spec}{\mathrm{spec}}

@@

\subsubsection{Proof of~\eqref{eqn:grid_sobolev_norm_higher_order}.}
To prove~\eqref{eqn:grid_sobolev_norm_higher_order}, we approximate the action $\wb{L}f(\wb{x})$ to within a factor of $h^s$ for all $\wb{x} \in \wb{X}$. The manner in which we do this depends on whether $\wb{x}$ is sufficiently in the interior, or conversely is near the boundary, of $\wb{X}$. With an appropriate approximation in hand, we then find the desired estimate on the discrete semi-norm $f^T \wb{L}^s f$.

@@

\subsection{Proof of Proposition~\ref{prop:L4_testing_rate}}

Let $T_{\mathrm{mean}} = \frac{1}{n}\sum_{i = 1}^{n} y_i^2$. The expectation of $T_{\mathrm{mean}}$ is
\begin{equation*}
\Ebb(T_{\mathrm{mean}}) = \mathbb{E}(f^2(x_1)) + 1,
\end{equation*}
and the variance can be upper bounded
\begin{equation*}
\Var(T_{\mathrm{mean}}) \leq \frac{1}{n}(3 + p_{\max} \norm{f}_{\Leb^4}^4 + p_{\max}\norm{f}_{\Leb^2}^2) = \frac{c}{n}.
\end{equation*}
Since $\mathbb{E}(f^2(x_1)) \geq p_{\min} \epsilon^2$, when $\epsilon^2 \gtrsim b\cdot n^{-1/2}$ we can apply Chebyshev's inequality to obtain the claimed result.

@@

For Lemmas~\ref{lem:expected_first_order_seminorm} - \ref{lem:expected_first_order_seminorm_3}, we will assume that $K$ is a kernel function compactly supported on $B(0,1)$ and upper bound $K(x) \leq K_{\max}$. Additionally, we note that although each Lemma assumes $g \in C^1(\Xset)$, in each case if we assume merely $g \in H^1(\Xset)$ the results still hold due to the density of $C^{\infty}$ in $H^1(\Xset)$.

>>>>

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\Xsetx}{\,dx}
\newcommand{\Xsety}{\,dy}
\newcommand{\Xsetr}{\,dr}
\newcommand{\Xsetxpr}{\,dx'}
\newcommand{\Xsetypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\spec}{\mathrm{spec}}

@@

\subsubsection{Proof of~\eqref{eqn:grid_sobolev_norm_higher_order}.}
To prove~\eqref{eqn:grid_sobolev_norm_higher_order}, we approximate the action $\wb{L}f(\wb{x})$ to within a factor of $h^s$ for all $\wb{x} \in \wb{X}$. The manner in which we do this depends on whether $\wb{x}$ is sufficiently in the interior, or conversely is near the boundary, of $\wb{X}$. With an appropriate approximation of $\wb{L} f(\wb{x})$ in hand, we then find the desired estimate on the discrete semi-norm $f^T \wb{L}^s f$.

@@

\subsection{Proof of Proposition~\ref{prop:L4_testing_rate}}
Let $T_{\mathrm{mean}} = \frac{1}{n}\sum_{i = 1}^{n} y_i^2$. The expectation of $T_{\mathrm{mean}}$ is
\begin{equation*}
\Ebb(T_{\mathrm{mean}}) = \mathbb{E}(f^2(x_1)) + 1,
\end{equation*}
and the variance can be upper bounded
\begin{equation*}
\Var(T_{\mathrm{mean}}) \leq \frac{1}{n}(3 + p_{\max} \norm{f}_{\Leb^4}^4 + p_{\max}\norm{f}_{\Leb^2}^2) = \frac{c}{n}.
\end{equation*}
Since $\mathbb{E}(f^2(x_1)) \geq p_{\min} \epsilon^2$, when $\epsilon^2 \gtrsim b\cdot n^{-1/2}$ we can apply Chebyshev's inequality to obtain the claimed result.

@@

For Lemmas~\ref{lem:expected_first_order_seminorm} - \ref{lem:expected_first_order_seminorm_3}, we will assume that $K$ is a kernel function compactly supported on $B(0,1)$ satisfying the upper bound $K(x) \leq K_{\max}$ for all $x \in B(0,1)$. Additionally, we note that although each Lemma assumes $g \in C^1(\Xset)$, in each case if we assume merely $g \in H^1(\Xset)$ the results still hold due to the density of $C^{\infty}$ in $H^1(\Xset)$.

### 2021-02-11 notes/weekly_notes/8.26.20.NotesForWeek.tex
Cleaned up notes folder.

\subsection{First-order graph Sobolev semi-norm.}
We begin by upper bounding $f_0^T \Lap_{n,r} f_0$ under the assumption $f_0 \in H^1(\Xset,M)$. This will be the easiest of the three Lemmas to prove, while still giving some sense of how the proofs develop in the more complicated cases. The upper bound will depend on the kernel $K$; we assume throughout that $K:[0,\infty) \to [0,\infty)$ is a $K_{\max}$-Lipschitz function supported on $[0,1]$, and without loss of generality that
\begin{equation*}
\int_{\Reals^d} K(\norm{z}) \,dz = 1.
\end{equation*}
\begin{lemma}
	\label{lem:first_order_graph_sobolev_seminorm}
	Suppose $\Xset$ is a Lipschitz domain, and that $p(x) \leq p_{\max}$ for all $x \in \Xset$. Then, for any $f \in H^1(\Xset,M)$, there exists a constant $C > 0$ which may depend only on $\Xset$ and $d$ such that
	\begin{equation}
	f^T \Lap_{n,r} f \leq \frac{C}{\delta} n^2 r^{d + 2} M^2
	\end{equation}
	with probability at least $1 - \delta$.
\end{lemma}
\begin{proof}
	We will show that
	\begin{equation*}
	\Ebb\Bigl[f^T \Lap_{n,r} f\Bigr] \leq C n^2 r^{d + 2} M^2,
	\end{equation*}
	whence the claim follows immediately by Markov's inequality (recall that $\Lap_{n,r}$ is positive semi-definite, and therefore $f^T \Lap_{n,r} f$ is a non-negative random variable).

	Since
	\begin{equation*}
	f^T \Lap_{n,r} f = \frac{1}{2}\sum_{i, j = 1}^{n} \bigl(f(X_i) - f(X_j)\bigr)^2 A_{ij},
	\end{equation*}
	it follows that
	\begin{equation}
	\label{pf:first_order_graph_sobolev_seminorm_1}
	\Ebb\Bigl[f^T \Lap_{n,r} f\Bigr] = \frac{n(n - 1)}{2} \Ebb\biggl[\Bigl(f(X') - f(X)\Bigr)^2 K_r(X',X)\biggr]
	\end{equation}
	where $X$ and $X'$ are random variables independently drawn from $P$.

	For the remainder of this proof, we will assume that $f \in C^{\infty}(\Xset)$, which we may do without loss of generality because $C^{\infty}(\Xset)$ is dense in $H^1(\Xset)$. Moreover, since $\Xset$ is a Lipschitz domain there exists an extension $g \in C^{\infty}(\Rd)$ of $f$ satisfying
	\begin{equation}
	\label{pf:first_order_graph_sobolev_seminorm_2}
	|g|_{H^1(\Rd)} \leq C|f|_{H^1(\Xset)} \leq C M,
	\end{equation}
	for a constant $C$ which may depend on $\Xset$ and $d$, but does not depend on $M$ or $f$. Since $g(x) = f(x)$ and $p(x) \leq p_{\max}$ for all $x \in \Xset$, 
	\begin{align}
	\Ebb\Bigl[\bigl(f(X') - f(X)\bigr)^2K_r(X',X)\Bigr] & = \Ebb\Bigl[\bigl(g(X') - g(X)\bigr)^2K_r(X',X)\Bigr] \nonumber \\
	& \leq p_{\max}^2 \int_{\Reals^d} \int_{\Reals^d} \bigl(g(x') - g(x)\bigr)^2 K_r(x',x) \,dx' \,dx. \label{pf:first_order_graph_sobolev_seminorm_3}
	\end{align}
	It remains only to bound the integral. Taking a first-order Taylor expansion of $g$, we get
	\begin{align*}
	\int_{\Reals^d} \int_{\Reals^d} \bigl(g(x') - g(x)\bigr)^2 K_r(x',x) \,dx \,dx' & = \int_{\Rd} \int_{\Rd} \biggl\{\sum_{\abs{\alpha} = 1}G_{\alpha}(x,x') (x' - x)^{\alpha}\biggr\}^2 K_r(x',x) \,dx' \,dx \\ 
	& \overset{(i)}{\leq}  \int_{\Rd} \int_{\Rd} \biggl\{\sum_{\abs{\alpha} = 1}\Bigl[G_{\alpha}(x,x')\Bigr]^2\biggr\} \norm{x' - x}^2  K_r(x',x) \,dx' \,dx \\
	& \overset{(ii)}{\leq} \int_{\Rd} \int_{\Rd} \biggl\{\int_{0}^{1} \sum_{\abs{\alpha} = 1} \Bigl[g^{(\alpha)}\bigl(x + t(x' - x)\bigr)\Bigr]^2 \,dt \biggr\} \norm{x' - x}^2 K_r(x',x) \,dx' \,dx \\
	& \overset{(iii)}{=} r^{2 + d} \int_{\Rd} \int_{B(0,1)} \biggl\{\int_{0}^{1} \sum_{\abs{\alpha} = 1} \Bigl[g^{(\alpha)}\bigl(x + trz\bigr)\Bigr]^2 \,dt\biggr\} \norm{z}^2 K\bigl(\norm{z}\bigr)  \,dz \,dx \\
	& \overset{(v)}{=} r^{2 + d} \int_{B(0,1)} \int_{0}^{1} \biggl\{\int_{\Rd} \sum_{\abs{\alpha} = 1} \Bigl[g^{(\alpha)}\bigl(x + trz\bigr)\Bigr]^2 \,dx \biggr\} \norm{z}^2 K\bigl(\norm{z}\bigr) \,dt \,dz \\
	& \leq r^{2 + d} |g|_{H^1(\Rd)}.
	\end{align*}
	In the above manipulations, $(i)$ follows by the Cauchy-Schwarz inequality, $(ii)$ follows by Jensen's inequality, $(iii)$ follows from the change of variables $z = (x' - x)/r$, and $(v)$ follows by Fubini's Theorem. Along with~\eqref{pf:first_order_graph_sobolev_seminorm_1}-\eqref{pf:first_order_graph_sobolev_seminorm_3}, this proves Lemma~\ref{lem:first_order_graph_sobolev_seminorm}.
\end{proof}

>>>>

\subsection{First-order graph Sobolev semi-norm.}
We begin by upper bounding $f_0^T \Lap_{n,r} f_0$ under the assumption $f_0 \in H^1(\Xset,M)$. This will be the easiest of the three Lemmas to prove, while still giving some sense of how the proofs develop in the more complicated cases. The upper bound will depend on the kernel $K$ through the quantity
\begin{equation*}
\sigma_K := \frac{1}{d}\int_{\Reals^d} \|z\|^2 K\bigl(\|z\|\bigr) \,dz
\end{equation*}

\begin{lemma}
	\label{lem:first_order_graph_sobolev_seminorm}
	For any $f \in H^1(\Xset)$, we have that
	\begin{equation}
	f^T \Lap_{n,r} f \leq \frac{p_{\max}^2 \sigma_K}{\delta} n^2 r^{d + 2} |f|_{H^1(\Xset)}^2
	\end{equation}
	with probability at least $1 - \delta$.
\end{lemma}
\begin{proof}
	We will show that
	\begin{equation*}
	\Ebb\Bigl[f^T \Lap_{n,r} f\Bigr] \leq p_{\max}^2 \sigma_K n^2 r^{d + 2} |f|_{H^1(\Xset)}^2
	\end{equation*}
	whence the claim follows immediately by Markov's inequality (recall that $\Lap_{n,r}$ is positive semi-definite, and therefore $f^T \Lap_{n,r} f$ is a non-negative random variable).

	Since
	\begin{equation*}
	f^T \Lap_{n,r} f = \frac{1}{2}\sum_{i, j = 1}^{n} \bigl(f(X_i) - f(X_j)\bigr)^2 \mathbf{W}_{ij},
	\end{equation*}
	it follows that
	\begin{equation}
	\label{pf:first_order_graph_sobolev_seminorm_1}
	\Ebb\Bigl[f^T \Lap_{n,r} f\Bigr] = \frac{n(n - 1)}{2} \Ebb\biggl[\Bigl(f(X') - f(X)\Bigr)^2 K\biggl(\frac{\|X' - X\|}{r}\biggr)\biggr]
	\end{equation}
	where $X$ and $X'$ are random variables independently drawn from $P$.

	For the remainder of this proof, we will assume that $f \in C^{\infty}(\Xset)$, which we may do without loss of generality because $C^{\infty}(\Xset)$ is dense in $H^1(\Xset)$ and the expectation on the right hand side of~\eqref{pf:first_order_graph_sobolev_seminorm_1} is continuous in $\Leb^2(\Xset)$. Obviously
	\begin{equation}
	\Ebb\biggl[\bigl(f(X') - f(X)\bigr)^2K\biggl(\frac{\|X' - X\|}{r}\biggr)\biggr] \leq p_{\max}^2 \int_{\Xset} \int_{\Xset} \bigl(f(x') - f(x)\bigr)^2 K_r(x',x) \,dx' \,dx. \label{pf:first_order_graph_sobolev_seminorm_2}
	\end{equation}
	and it remains now to bound the integral. Taking a first-order Taylor expansion of $f$, we get
	\begin{align}
	\int_{\Xset} \int_{\Xset} \bigl(f(x') - f(x)\bigr)^2 K_r(x',x) \,dx' \,dx & = \int_{\Xset} \int_{\Xset} \biggl[\int_{0}^{1} \nabla f\bigl(x + t(x' - x)\bigr)^T (x' - x)\,dt\biggr]^2 K\biggl(\frac{\|x' - x\|}{r}\biggr) \,dx' \,dx \nonumber \\
	& \overset{(i)}{\leq} \int_{\Xset} \int_{\Xset} \int_{0}^{1} \biggl[\nabla f\bigl(x + t(x' - x)\bigr)^T (x' - x)\biggr]^2 K\biggl(\frac{\|x' - x\|}{r}\biggr) \,dt\,dx' \,dx \nonumber \\
	& \overset{(ii)}{=} r^{d + 2} \int_{\Xset} \int_{\mc{Z}_r(x)} \int_{0}^{1} \biggl[\nabla f\bigl(x + trz\bigr)^T z\biggr]^2 K\bigl(\|z\|\bigr) \,dt\,dz \,dx \\
	&  \overset{(iii)}{\leq} r^{d + 2} \int_{\Xset} \int_{\Reals^d} \int_{0}^{1} \Bigl[\nabla f\bigl(\wt{x}\bigr)^T z\Bigr]^2 K\bigl(\|z\|\bigr) \,dt \,dz \,d\wt{x} \nonumber \\
	& = r^{d + 2} \int_{\Xset} \int_{\Reals^d} \Bigl[\nabla f\bigl(\wt{x}\bigr)^T z\Bigr]^2 K\bigl(\|z\|\bigr) \,dz \,d\wt{x} \label{pf:first_order_graph_sobolev_seminorm_3}
	\end{align}
	where $(i)$ follows by Jensen's inequality, $(ii)$ follows by substituting $z = (x' - x)/r$ with $\mc{Z}_r(x) := \{z: zr + x \in \Xset\}$ and $(iii)$ by substituting $\wt{x} = x + trz$ and noting that
	\begin{equation*}
	x \in \Xset ~~\textrm{and}~~ z \in \mc{Z}_r(x) \Longrightarrow x + trz \in \Xset ~~\textrm{and}~~ z \in \Reals^d.
	\end{equation*}
	Now, writing $\bigl(\nabla f(\wt{x}) ^T z\bigr)^2 = \bigl(\sum_{i = 1}^{d} f^{(e_i)}(x) z_{i}\bigr)^2$, expanding the square and integrating, we have that for any $\wt{x} \in \Xset$,
	\begin{align*}
	\int_{\Reals^d} \Bigl[\nabla f\bigl(\wt{x}\bigr)^T z\Bigr]^2 K\bigl(\|z\|\bigr) \,dz & = \sum_{i,j = 1}^{d} f^{(e_i)}(\wt{x}) f^{(e_j)}(\wt{x}) \int_{\Rd} z_iz_jK(\|z\|) \,dz \\
	& = \sum_{i = 1}^{d} \bigl(f^{(e_i)}(\wt{x})\bigr)^2 \int_{\Rd} z_i^2 K\bigl(\|z\|\bigr) \,dz \\
	& = \sigma_K \|\nabla f(\wt{x})\|^2
	\end{align*}
	and by plugging back into~\eqref{pf:first_order_graph_sobolev_seminorm_3}, we obtain the claimed result.
\end{proof}
